Bird beak's elaboration and exploration

### 2021-05-28 Analysis/equations.tex
equation draft board

>>>>

For any vectors $\vec{a}$ and $\vec{b}$, defined either as one set or a pair of sets of coordinates in $n$ dimensions:

\begin{equation}
    \vec{a} = 
    \begin{bmatrix}
    x \\
    y \\
    ... \\
    n \\
    \end{bmatrix}
\end{equation}

\begin{equation}
    \vec{a} = 
    \begin{bmatrix}
    x_{1} & x_{2} \\
    y_{1} & y_{2} \\
    ... & ... \\
    n_{1} & n_{2} \\
    \end{bmatrix}
\end{equation}

We can calculate $\vec{a_{1}}$, the orthogonal projection of $\vec{a}$ onto $\vec{b}$ using:

\begin{equation}
    \vec{a_{1}} = \frac{\vec{a} \cdot \vec{b}}{\|\vec{b}\|}
\end{equation}

With $\|\vec{b}\| = \sqrt{\vec{b} \cdot \vec{b}}$ being the norm of $\vec{b}$.

 And $\vec{a_{2}}$, the rejection of $\vec{a}$ onto $\vec{b}$:

\begin{equation}
    \vec{a_{2}} = \vec{a} - \vec{a_{1}}
\end{equation}

And $\theta$, the angle formed by $\vec{a}$ and $\vec{b}$:

\begin{equation}
    \theta = acos \left(\frac{\vec{a} \cdot \vec{b}}{\|\vec{a}\| \cdot \|\vec{b}\|} \right)
\end{equation}

Given a $n$ dimensional trait space $TS_{m,n}$ with $m$ elements defined as:

\begin{equation*}
TS_{m,n} = 
    \begin{bmatrix}
        x_{1} & x_{2} & \cdots & x_{m} \\
        y_{1} & y_{2} & \cdots & y_{m} \\
        \vdots  & \vdots  & \ddots & \vdots  \\
        n_{1} & n_{2} & \cdots & n_{m} \\
    \end{bmatrix}
\end{equation*}

And a base vector $B_{n}$ defined as:

\begin{equation*}
B_{n} = 
    \begin{bmatrix}
        Bx_{1} & Bx_{2}\\
        By_{1} & By_{2}\\
        \vdots  & \vdots \\
        Bn_{1} & Bn_{2}\\
    \end{bmatrix}
\end{equation*}

\begin{equation}
        cTS = TS - [Bx_{1}, By_{1}, \cdots, Bn_{1}]^{\text{T}}
\end{equation}

\begin{equation}
I_{\vec{B}} - \vec{B}\vec{B}^\text{T} - \vec{\hat{\imath}}\vec{\hat{\imath}}^\text{T} + [\vec{B} \vec{\hat{\imath}}]     \begin{bmatrix}
        cos(\theta) & -sin(\theta)\\
        sin(\theta) & cos(\theta)\\
    \end{bmatrix} [\vec{B} \vec{\hat{\imath}}]^\text{T}
\end{equation}

Where $\theta$ is:

\begin{equation}
    \theta = acos \left(\frac{\vec{B} \cdot \vec{\hat{\imath}}}{\|\vec{B}\| \cdot \|\vec{\hat{\imath}}\|} \right)
\end{equation}

Or $\theta = acos (B_x)$ since both \|\vec{B}\| and \|\vec{\hat{\imath}}\| are equal to 1 and \|\vec{\hat{\imath}}\| is the unit vector on the first axis.
